### 2019-01-06 draft.tex
abstract and keywords

>>>>

\section*{Abstract}

% Currently 236 words
Hybrid offspring of diverged species often experience reduction in fitness relative to either individuals from either parental population. In some cases, species evolve increased premating isolation in order to prevent the production of these low fitness hybrids in a process known as reinforcement. Theoretical challenges to the evolution of reinforcement are generally cast as a coordination problem – e.g. how can linkage disequilibrium between trait and preference loci be maintained in the face of recombination.  However, the evolution of reinforcement also poses a potential conflict between mates, for example when the opportunity costs to interspecific hybridization differ between the sexes or species. This is particularly likely for postmating prezygotic isolation, as male gametes can only increase their fitness by fertilizing heterospecific eggs. We develop a population genetic model of this interspecific conflict over reinforcement, and a complimentary model which lacks this conflict. We demonstrate that this conflict results in the transient evolution of reinforcement– after a female preference for conspecific gamete trait rises to high frequency, such traits adaptively introgress into the other population. Ultimately the gamete trait fixes in both species, and prezygotic isolation returns to pre-reinforcement levels. This transience is not observed without conflict. We suggest that interspecific conflict over reinforcement provides an obstacle to the evolution of postmating prezygotic isolation, and focus on the gametophytic factor loci in hybridizing. populations of maize and teosinte as a case likely experiencing this conflict. 
\\ 
\\ 
\\ 
\textit{keywords:} Reinforcement, Sexual conflict, Speciation, Hybridization

\newpage
